\textit{Monami} as an oscillatory hydrodynamic instability in a submerged sea grass bed

### 2014-10-22 Paper/cover.tex
Fixed spelling in cover letter

Our analysis shows that the existing explanation for these oscillations is incorrect. The existing explanation invokes the existence of a shear layer near the top of the grass bed, which is established due to the drag exerted by the grass of the flow. This shear layer is assumed to be unstable to the Kelvin-Helmholtz instability; the vortices that form as a result of this instability then drive the synchronous oscillations of the grass blades. We test this explanation mathematically in our manuscript, using a self-consistent linear stability analysis of the flow. We demonstrate that indeed the steady flow is hydrodynamically unstable and the instability mechanism, although superficially similar to the Kelvin-Helmholtz instability, is in fact distinct from it. The results from our model are supported by qualitative observations in the field and quantitative lab experiments reported in the literature.

>>>>

Our analysis shows that the existing explanation for these oscillations is incorrect. The existing explanation invokes the existence of a shear layer near the top of the grass bed, which is established due to the drag exerted by the grass on the flow. This shear layer is assumed to be unstable to the Kelvin-Helmholtz instability; the vortices that form as a result of this instability then drive the synchronous oscillations of the grass blades. We test this explanation mathematically in our manuscript, using a self-consistent linear stability analysis of the flow. We demonstrate that indeed the steady flow is hydrodynamically unstable and the instability mechanism, although superficially similar to the Kelvin-Helmholtz instability, is in fact distinct from it. The results from our model are supported by qualitative observations in the field and quantitative lab experiments reported in the literature.
